ISYE 6501

### 2022-09-28 hw5-1/submission.Rmd
submission v2

1.  Dropping variables: U1, M.F and U2
2.  number of trees = 40
3.  mtry = 4

@@

```{r}
rf_final_model <- randomForest(Crime ~ . -U1 -M.F -U2, data = crime_df, ntree = 40, mtry=4, importance = TRUE)
rmse_func(true=crime_df$Crime,predicted = rf_final_model$predicted)
```

@@

@@

We can observe that dropping statistically insignificant features help us achieve a higher AUC value. Hence this increases our model's ability to separate between the classes.

@@

We can use the F-Beta value for determining the best value of threshold. As we are given that a classifying a "bad" customer as "good" is 5 times worse than classifying "good" customer as "bad". We need to determine the best value of threshold that will help us increase recall and accordingly lower the value of false negatives (positive class is 1 i.e. "bad").

@@

@@

@@

By choosing our threshold to be 0.11, we can achieve a recall value of 0.91. While our precision has gone down, we are not making mistakes with false negatives which are more costly to us.

In our test data, the no. of "bad" classified data points was ~33%. We were able to achieve a threshold value of 0.11 which is 1/3rd of that value.

>>>>

1.  Dropping variables: U1, M.F and U2
2.  number of trees = 40
3.  mtry = 3

@@

```{r}
rf_final_model <- randomForest(Crime ~ . -U1 -M.F -U2, data = crime_df, ntree = 40, mtry=3, importance = TRUE)
rmse_func(true=crime_df$Crime,predicted = rf_final_model$predicted)
```

@@

If we want we can still test if drop the lowest variables: Time and Pop is helpful.

@@

We can observe that dropping statistically insignificant features help us achieve a higher AUC value, which translates to a better risk discrimination. In other words, this increases our model's ability to separate between the classes.

@@

We can use the F-Beta value for determining the best value of threshold. As we are given that a classifying a "bad" customer as "good" is 5 times worse than classifying "good" customer as "bad". We need to determine the best value of threshold that will help us increase recall (positive class is 1 i.e. "bad").

@@

```{r}
ggplot(rp.df, aes(threshold)) + 
  geom_line(aes(y = precision, colour = "precision")) + 
  geom_line(aes(y = recall, colour = "recall"))
```

As expected, decreasing threshold, makes it easier to classify data points as bad, and so our recall value increases. On the other hand, because on longer threshold, we might no longer be tagging the actual bads, our model precision decreases.

Also the Precision and Recall curver intersect somewhere between 0.3 to 0.4, which is near the bad rate in our dataset.

@@

$$
Error Rate^* = \frac{5.FP}{TP+FP+FN+TN} + \frac{FN}{TP+FP+FN+TN}
$$

\*Note we are deviating here from conventional deviation of error rate, in order to better apply to our use case.

@@

By choosing our threshold to be 0.11, we can achieve a recall value of 0.91, which implies if there are 100 "bad" points we are able to capture 91 of those.

It is also interesting to note here, that the we have \~33% "bad" data points. We

In our test data, the no. of "bad" classified data points was \~33%. We were able to achieve a threshold value of 0.11 which is 1/3rd of that value.
